\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{xcolor}
\usepackage{fontawesome}
\usepackage{hyperref}


\input{glyphtounicode}

% -------------------- FONT --------------------
\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-1in} % Default was -.5in
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Section formatting
\titleformat{\section}{
  \vspace{-5pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Subsection formatting
\titleformat{\subsection}{
  \vspace{-4pt}\scshape\raggedright\large
}{\hspace{-.15in}}{0em}{}[\color{black}\vspace{-8pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

% -------------------- CUSTOM COMMANDS --------------------
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\setlength{\footskip}{4.08003pt}

% -------------------- START OF DOCUMENT --------------------
\begin{document}

% -------------------- HEADING--------------------
\begin{flushright}
  \vspace{-4pt}
\end{flushright}

\vspace{-7pt}

\begin{center}
    \textbf{\Huge \scshape Pavan Kanakkassery} \\ \vspace{8pt}
    \small 
    %\faGithub
    %\href{https://github.com/johnDoe}{\underline{github.com/johnDoe}} $  $
    %\faCode $  $
    %\href{https://www.johndoe.com}
    %{\underline{johndoe.com}} $  $
    \faEnvelope$  $
    \href{mailto:pkanakka@nyit.edu}
    {\underline{pkanakka@nyit.edu}}
    \faPhone$  $
    \underline{845-689-4491}
    \faLinkedin$  $
    \href{https://linkedin.com/in/pavankanakkassery}{\underline{linkedin.com/in/pavankanakkassery}} $  $
\end{center}

% -------------------- EDUCATION --------------------
\section{Education}
  \resumeSubHeadingListStart
  
    \resumeSubheading
      {New York Institute of Technology}{May 2026}
      {Bachelor of Science in Electrical and Computer Engineering}{Current GPA: 3.9/4.0}
      
      \resumeItemListStart 
      \resumeItem{Relevant Coursework:} {Digital Systems, Microprocessors, Control Systems, Embedded Systems, Signal Processing} 
      \resumeItem{Presidential Honors List:} {For Fall 2022 to Spring 2024} 
      \resumeItem{Extracurricular Activities:} {Member of IEEE Student Branch; Volunteer at local STEM outreach programs} 
      \resumeItemListEnd
      
    \resumeSubheading
      {Briarcliff Manor High School }{June 2022 - May 2022}
      {High School Diploma}{GPA: 3.7/4.0}
      

  \resumeSubHeadingListEnd

% -------------------- SKILLS --------------------
\section{Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
    
     \textbf{Programming Languages}{: Python, Java, Matlab C, HTML/CSS} \\
     
     \textbf{Software Tools / Libraries}{: PSpice, LTSpice, IntelliJ IDEA, AutoCAD, pandas, NumPy, Git/GitHub,  VS Code} \\

     \textbf{Languages}{: English, Malayalam, Hindi} \\
     
    }}
 \end{itemize}

% -------------------- EXPERIENCE --------------------
\section{Professional Experience}
  \resumeSubHeadingListStart

        \resumeProjectHeading
        {\textbf{Securitas Technology} $|$ \footnotesize\emph{Engineering Intern}}{June 2024 -- Present}
        \resumeItemListStart
          \resumeItem{Collaborated with engineers to develop precise technical drawings and models, ensuring accuracy and adherence to project specifications.}
          \resumeItem{Utilized advanced CAD software to design and optimize components and systems, enhancing efficiency and performance.}
          \resumeItem{Gained practical experience in engineering design processes and technologies, contributing to real-world projects.}
          \resumeItem{Contributed to projects involving Google, AWS, and Microsoft datacenters, applying engineering principles to optimize infrastructure and systems.}
          \resumeItem{\textbf{\textit{TECH STACK: Bluebeam Revu, AutoCAD}}}
        \resumeItemListEnd

        \resumeProjectHeading
        {\textbf{New York Institute of Technology} $|$ \footnotesize\emph{Undergraduate Student Researcher}}{September 2023 -- Present}
        \resumeItemListStart
          \resumeItem{Member researching the energy enhancement in analog to digital converters for wearable
          biomedical devices using data records from the MIT-BIH Arrhythmia database.}
          \resumeItem{Collaborated with research team members weekly to code and advance design functions that
          can be used to map the ECG signal output signal output in a patient's heart.}
          \resumeItem{Developed algorithms to enhance the accuracy and efficiency of ECG signal processing, contributing to the advancement of wearable biomedical technology.}
        \resumeItemListEnd
 
    \resumeSubHeadingListEnd 


% -------------------- PROJECTS --------------------
\section{Projects}
    \resumeSubHeadingListStart
    
        \resumeProjectHeading
        {\textbf{\href{https://github.com/pjk132020/The-Flappy-Bird-Carousel.git}{\underline{The Flappy Bird Carousel\faExternalLink}}} $|$ \footnotesize\emph{Hack UMASS}}{}
        \resumeItemListStart
            \resumeItem{Developed a rotating platform arcade game using Arduino boards, stepper and servo motors, merging modern tech with retro gaming elements.}
            \resumeItem{Tackled engineering challenges like wire tangling by rotating the microcontroller, showcasing resilience and adaptability.}
            \resumeItem{Gained expertise in Arduino IDE for motor control and collaborated effectively to create a functional prototype, laying the groundwork for future enhancements.}

        \resumeItemListEnd
          
    \resumeSubHeadingListEnd

% -------------------- EXPERIENCE --------------------
\section{Extracurricular Activities}
  \resumeSubHeadingListStart
        \resumeProjectHeading
          {\textbf{Volleyball Youth Team} $|$ \footnotesize\emph{Team Leader}\vspace{8pt}}{August 2024}
          {\small{Currently leading a team of 10-15 youth members, fostering teamwork and preparing for upcoming tournaments.}}
    
        \resumeProjectHeading
          {\textbf{Zebra Technologies Student Meetup} $|$ \footnotesize\emph{Attendee}\vspace{8pt}}{October 2024}
          {\small{Participated in an insightful company visit, gaining firsthand knowledge of industry practices and networking with professionals to enhance my understanding of the field.}}        

    \resumeSubHeadingListEnd 


\end{document}
